A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Figure legend update
Work in progress
Figure legend upgrade
Work in progress
Proposal and discussion improvement.

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their own. Our focus was not on a single animal species but all of them, using
general abstraction to identify what those species have in common.

@@

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. The general model concept is shown on the Fig.~\ref{fig2}.

@@

>>>>

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their own. Our focus was not on a single animal species but all of them, using
general abstraction to identify what those species have in common. Some
questions in our train of thought were:

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\cdot$] How does nature work?
    \item[$\cdot$] Is evolution real?
    \item[$\cdot$] How do we enforce natural selection in evolution?
    \item[$\cdot$] What is the role of the attraction between couples on reproduction?
    \item[$\cdot$] How much of a factor is the attraction's role in the evolution of the species?
    \item[$\cdot$] What is the role of death in all of this?
    \item[$\cdot$] How much of an impact does death have on the evolution of a species?
    \item[$\cdot$] How do we include those ideas into our algorithm?
\end{description}

@@

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. The general model concept is shown in Figure~\ref{fig2}.

@@

At some crucial moments during our research, we got the feeling we were doing
nature reverse engineering. One strategy was to let our imagination run wild
and go for the simple solution. One of our earlier experiment's findings was to
find balance, like the yin and yang, between death and reproduction.
